Big Ideas in Sports Analytics and Statistical Tools for their Investigation

### 2022-06-14 sports_analytics.Rmd
a paragraph on nfl wp

```{r pkg}
knitr::write_bib(
  c(
    "base",
    "Lahman", "pitchRx", "retrosheet",
    "teamcolors",
    "ggplot2",
    "BradleyTerry2"
  ),
  file = "pkgs.bib"
)
```

@@

# Win probability

@@

In football,

Burke WPA

http://www.advancedfootballanalytics.com/2010/01/win-probability-added-wpa-explained.html

@Lock2014 used random forests as a means for estimating WP before each play in a football game.

@Yurko2019

@@

nflscrapr, nflfastR, nflverse

@@

>>>>

```{r pkg}
knitr::write_bib(
  c(
    "base",
    "Lahman", "pitchRx", "retrosheet",
    "teamcolors",
    "ggplot2",
    "BradleyTerry2",
    "nflfastR",
    "nflverse"
  ),
  file = "pkgs.bib"
)
```

@@

# Win probability {#sec:wp}

@@

In recent years, a number of statistical methods have been used to build well-calibrated win probability models in American football. @Lock2014 used random forests as a means for estimating win probability before each play in a football game. In addition, @Yurko2019 estimated win probability in the NFL using a generalized additive model, as part of the `nflscrapr` package and nflwar framework. A major highlight of this framework is it is fully reproducible and uses publicly available data. One of @Yurko2019's goals was also to encourage researchers to "use, explore, and improve upon our work", which ultimately inspired \pkg{nflfastR}, known as the successor to `nflscrapr`

(add a wp example from nflfastR)

@@

@@

ann appl stat march 2022 paper on wp in rugby

https://projecteuclid.org/journals/annals-of-applied-statistics/volume-16/issue-1/In-game-win-probabilities-for-the-National-Rugby-League/10.1214/21-AOAS1514.short
